### 2023-03-14 paper.tex
update discussion

\section{note to Simon: this is how far I got}   % todo rm

@@

Furthermore, we show a way to pinpoint minimal regions of high variability across cells, which we call variably methylated regions (VMRs).
By re-analyzing two published data sets, we could show that these improvements to data preprocessing help to increase signal and decrease noise, resulting in a more informative intermediate-dimensional representation of the data.
As examples of practical benefits, we demonstrate that our preprocessing allows for better distinction of cell sub-types, especially for smaller data sets with a limited number of cells.
In addition to this improvement of global signal-to-noise ratio (with regards to cell dissimilarity quantification), we also show that the determination of VMRs improve biological interpretability by pinpointing the regions that actually change and hence have a putative regulatory role.

@@

In addition, by pinpointing exact regions of interest, the VMR functionality provides useful input for genomics-style analyses.
Depending on the research question at hand, individual VMRs can be related to nearby genomic features such as gene bodies or known regulatory elements, tested for methylation differences between groups of cells, or subjected to gene ontology enrichment or motif enrichment.

@@

\phantomsection
\section{Methods}

>>>>

@@

Furthermore, we show a way to pinpoint minimal regions of high variability across cells, which we call variably methylated regions (VMRs).
By re-analyzing two published data sets, we could show that these improvements to data preprocessing help to increase signal and decrease noise, resulting in a more informative intermediate-dimensional representation of the data.
As examples of practical benefits, we demonstrate that our preprocessing allows for better distinction of cell sub-types, especially for challenging data sets comprising cellular sub-states and lineage transitions.

To furthermore aid interpretation of scBS data, we developed and implemented the first single-cell DMR detection algorithm.
FDR estimation via permutation allows us to report statistical significance of each DMR.
% maybe here discuss pseudoreplication issues?
Applying our approach to NSCs and oligodendrocytes demonstrated that the obtained DMRs locate near meaningful loci associated with cell-type specific functions.
Thus, our method aids biological interpretability by pinpointing the regions that differ between groups of cells and hence have a putative regulatory role.

@@

In addition, by pinpointing exact regions of interest, the VMR and DMR functionalities provide useful input for genomics-style analyses.
Depending on the research question at hand, individual DMRs can be related to nearby genomic features such as gene bodies or known regulatory elements, tested for methylation differences between groups of cells, or subjected to gene ontology enrichment or motif enrichment.

@@

\phantomsection
\section{Methods (note to Simon: didnt go through this yet)}  % todo rm
